---
title: "Homework Assignment 01"
subtitle: "Numerical Statistics Fall, 2021"
author: "Jake Underland"
date: "`r Sys.Date()`"
output:
  pdf_document: 
    latex_engine: pdflatex
    toc: false
    extra_dependencies: ["amsmath", "xcolor", "bm"]
    keep_tex: yes
  html_document:
    toc: false
    toc_depth: 3
    toc_float: yes
  word_document:
    toc: false
    toc_depth: '3'
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. 
Calculate the arithmetic mean $\bar{x_5}$ of a data $4, 6, 8, 9, 13$ and then express it in the form of an irreducible fraction or an integer.  

\textit{Solution.}  
$$\begin{aligned}
\bar{x_5} &= \frac{4+ 6+ 8+ 9+ 13}{5} = \frac{40}{5} = 8
\end{aligned}$$

## 2.  
Suppose we draw a sample of size $16$ from a finite population of size $65$, where sampling is without replacement. Calculate the finite population correction factor $FPC$ and then express it in the form of a decimal to the third decimal places.  

\textit{Solution.}  
$$FPC_{N, n} = \sqrt{\frac{N-n}{N-1}}, \: N = 65, \: n = 16$$
$$FPC_{65,16} = \sqrt{\frac{65-16}{65-1}} = \sqrt{\frac{49}{64}} = \frac{7}{8} = 0.875$$

```{r, include=FALSE}
fpc <- function(N, n) {
  x <- sqrt((N - n) / (N - 1))
  return(x)
}
r <- fpc(65, 16)
```

## 3.  
Suppose $X_1, X_2, X_3, X_4, X_5 \stackrel{i.i.d.}{\sim} Ber (0.4)$. Calculate the probability of the outcome $\{X_1 =0, X_2 = 0, X_3 = 1, X_4 = 0, X_5 = 1\}$ and then express it in the form of a decimal to the fifth decimal places.  

\textit{Solution.}  
$$\begin{aligned}
P(X_1 = 0, X_2 = 0, X_3 = 1, X_4 = 0, X_5 = 1)
&= P(X_1 = 0) P(X_2 = 0) P(X_3 = 1) P(X_4 =0) P(X_5 = 1) \\
&= p^2(1-p)^3 \\
&= (0.4)^2(0.6)^3 \\
&= 0.03456
\end{aligned}$$

## 4.  
Consider a data $(x_1, x_2, x_3, x_4) = (-5, a, 1, b) \;(-5 < a < 1 < b)$ whose arithmetic mean and variance are $2$ and $\frac{77}{2}$, respectively. Find the real numbers $a$ and $b$.  

\textit{Solution.}  
From the formula for the arithmetic mean, we have
$$\begin{aligned}
\frac{-5 + a + 1 + b}{4} &= 2 \\
-5 + a + 1 + b &= 8 \\
b &= 12 - a\\
\end{aligned}$$

Plug the value of $b$ into the equation for variance:
$$\begin{aligned}
\frac{(-5 - 2)^2 + (a-2)^2 + (1-2)^2 + (12-a-2)^2}{4} &= \frac{77}{2}\\
49 + a^2 -4a + 4 + 1 + 100 - 20a + a^2 &= 154 \\
2a^2 - 24a &= 0 \\
a(12-a) &= 0 \\
\implies \begin{cases}a = 0 \\ b = 12 \end{cases}, \begin{cases} a = 12 \\ b = 0 \end{cases}&
\end{aligned}$$
Since $-5 < a < 1 < b$, we can rule out the case where $a = 12, b = 0$, leaving us with 
$$a = 0, \;b = 12\dots \Box$$

## 5.  
Suppose we have a data $x_1, x_2, \dots , x_n$ of size $n$. Prove that the inequality
$$\sum_{i=1}^n(x_i-c)^2 \ge \sum_{i=1}^n(x_i-\bar{x})^2$$
holds for any real number $c$, where $\bar{x}$ is the arithmetic mean.  

\textit{Solution.}  
In order to prove $\sum_{i=1}^n(x_i-c)^2 \ge \sum_{i=1}^n(x_i-\bar{x})^2$, we first show $\sum_{i=1}^n(x_i-c)^2 - \sum_{i=1}^n(x_i-\bar{x})^2 \ge 0$. 
$$\begin{aligned}
\sum_{i=1}^n(x_i-c)^2 - \sum_{i=1}^n(x_i-\bar{x})^2 &= \sum_{i=1}^nx_i^2 - \sum_{i=1}^nx_i^2 - 2c\underbrace{\sum_{i=1}^nx_i}_{n\bar{x}} + 2\bar{x} \underbrace{\sum_{i=1}^nx_i}_{n\bar{x}} + nc^2 -n\bar{x}^2\\
&= -2cn\bar{x} + 2n\bar{x}^2 + nc^2 - n \bar{x}^2 \\
&= n(\bar{x}^2 -2c\bar{x}+ c^2) \\
&= n(\bar{x} - c)^2 \ge 0
\end{aligned}$$
Where the last inequality holds because $n \ge 0$ by definition and $(\bar{x} - c)^2$ is squared and thus at least $0$. Then, we have proven that 

$$\sum_{i=1}^n(x_i-c)^2 - \sum_{i=1}^n(x_i-\bar{x})^2 \ge 0$$
From which follows: 
$$\sum_{i=1}^n(x_i-c)^2 \ge \sum_{i=1}^n(x_i-\bar{x})^2 \dots \Box$$















