---
title: "Homework Assignment 02"
subtitle: "Numerical Statistics Fall, 2022"
author: Jake Underland - 1A193008
date: "`r Sys.Date()`"
output:
  pdf_document: 
    latex_engine: pdflatex
    toc: false
    extra_dependencies: ["amsmath", "xcolor", "bm"]
    keep_tex: yes
  html_document:
    toc: false
    toc_depth: 3
    toc_float: yes
  word_document:
    toc: false
    toc_depth: '3'
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE, echo = FALSE}
library(reticulate)
```


# 1.  
 Consider a stock that grows by 12\% in year one, declines by 8\% in
year two, declines by 3\% in year three and grows by 42\% in year four. In this case calculate the average growth rate of the stock, and then express it in the form of a decimal to the second decimal places. (When calculating the fourth root of a number using a calculator, you need only apply the square root twice.) (2 points)  

**Solution**:  

$$\sqrt[4]{(1 + 0.12) \times (1 - 0.08) \times (1 - 0.03) \times (1 + 0.42)} \approx 1.09\dots \Box$$

```{r}
sqrt(sqrt(1.12 * (1 - 0.08) * (1 - 0.03) * (1 + 0.42)))
```

# 2.  

Suppose we want to make a histogram based on a data $x_1, x_2, \dots, x_{128}$
using the Sturges rule, where we expect the histogram to be symmetrical. In this case find the number of classes, $k$, in the corresponding frequency distribution. (2 points)  
  

**Solution**: 
  
$$ k \approx 1 + \log_2 128 = 8\dots \Box$$
```{r}
1 + log(128, 2)
```

# 3.  

Consider the linear regression of $y$ on $x$ based on a data:
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
$x$ & 0 & 1 & 2 & 3 & 4 \\
\hline 
$y$ & 2 & 1 & 4 & 3 & 5 \\
\hline
\end{tabular}
Using the Pearson’s correlation coefficient $r_{xy}$, calculate the coefficient of determination $R^2$ of the regression, and then express it as an irreducible fraction. (7 points)   
  
**Solution**: 
  
\begin{align*} \bar{x} &= \frac{(0 + 1 + 2 + 3 + 4)}5  =2\\
\bar{y} &= \frac{(2 + 1 + 4 + 3 + 5)}5 = 3
\end{align*}

$$\begin{array}{ccccccc}
x & y & x - \bar{x} & y - \bar{y} & (x - \bar{x})(y - \bar{y}) & (x - \bar{x})^2 & (y - \bar{y})^2 \\
\hline 
0 & 2 & -2 & -1 & 2 & 4 & 1 \\
1 & 1 & -1 & -2 & 2 & 1 & 4 \\
2 & 4 & 0  &  1 & 0 & 0 & 1 \\
3 & 3 & 1  &  0 & 0 & 1 & 0 \\
4 & 5 & 2  &  2 & 4 & 4 & 4 \\
\hline 
\text{Total} && 0 & 0 & 8 & 10 & 10
\end{array}$$

\hfill$\underline{\implies r_{xy} = \frac{8}{\sqrt{10\times 10}} = \frac{4}{5}} \ldots\Box$

# 4.  

Suppose that six people, a, b, c, d, e and f, entered
their paintings in an exhibition, and judges X and Y scored the paintings within the range of 0 to 50 points and 0 to 100 points, respectively:
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
&a&b&c&d&e&f\\
\hline
X&50&45&25&30&35&10\\
\hline
Y&96&75&88&54&29&42 \\
\hline
\end{tabular}
In this case, calculate the Kendall rank correlation coefficient $r_k$, and then express it as an irreducible fraction. (9 points)  
  
**Solution**: 

The above data points ranked are as below: 
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
&a&b&c&d&e&f\\
\hline
X&6&5&2&3&4&1\\
\hline
Y&6&4&5&3&1&2 \\
\hline
\end{tabular}

Since there are 6 data points, the sum of the number of concordant pairs ($C$) and discordant pairs ($D$) is $C + D = {6\choose 2} = \frac{6\cdot 5}{2} = 15$. I count the number of concordant and discordant pairs below, using the given definition: 

```{python}
def countCD(data):
  C = D = 0
  for i, tup1 in enumerate(data[:-1]):
    for tup2 in data[i+1:]:
      if (tup1[0] > tup2[0] and tup1[1] > tup2[1]) \
      or (tup1[0] < tup2[0] and tup1[1] < tup2[1]):
        C += 1
      else:
        D += 1
  return C, D
```


\newpage 

```{python}
data = [(6, 6), (5, 4), (2, 5), (3, 3), (4, 1), (1, 2)]

print "Number of concordant pairs is:", countCD(data)[0], \
"\nNumber of discordant pairs is:", countCD(data)[1]
```

Thus, using the formula for the Kendall rank correlation coefficient, 
$$r_k = \frac{C - D}{C + D} = \frac{10 - 5}{15} = \frac{1}{3}\dots \Box$$













