---
title: "Homework Assignment 04"
subtitle: "Numerical Statistics Fall, 2022"
author: Jake Underland - 1A193008
date: "`r Sys.Date()`"
output:
  pdf_document: 
    latex_engine: pdflatex
    toc: false
    extra_dependencies: ["amsmath", "xcolor", "bm"]
    keep_tex: yes
  html_document:
    toc: false
    toc_depth: 3
    toc_float: yes
  word_document:
    toc: false
    toc_depth: '3'
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE, echo = FALSE}
library(reticulate)
```


# 1.  
Consider the set of data $\{(x_i,y_i)|i=1, 2, \dots, 6\} = \{(-2, -3), (-1, 0), (0, 1), (2, 3), (3, 4), (4, 7)\}$.  

\begin{enumerate}
\item[(1-1)] Find the Pearson correlation coefficient $r_{xy}$ based on the data.
\newline
\textbf{Solution.}\newline
\begin{align*} \bar{x} &= \frac{(-2 + -1 + 0 + 2 + 3 + 4)}6  =1\\
\bar{y} &= \frac{(-3 + 0 + 1 + 3 +4 + 7)}6 = 2
\end{align*}

$$\begin{array}{ccccccc}
x & y & x - \bar{x} & y - \bar{y} & (x - \bar{x})(y - \bar{y}) & (x - \bar{x})^2 & (y - \bar{y})^2 \\
\hline 
-2 & -3 & -3 & -5 & 15 & 9 & 25 \\
-1 & 0 & -2 & -2 & 4 & 4 & 4 \\
0 & 1 & -1  &  -1 & 1 & 1 & 1 \\
2 & 3 & 1  &  1 & 1 & 1 & 1 \\
3 & 4 & 2  &  2 & 4 & 4 & 4 \\
4 & 7 & 3  &  5 & 15 & 9 & 25 \\
\hline 
\text{Total} && 0 & 0 & 40 & 28 & 60
\end{array}$$

\hfill$\underline{\implies r_{xy} = \frac{40}{\sqrt{28\times 60}} = \frac{2\sqrt{105}}{21}} \ldots\Box$

\item[(1-2)] Find the linear regression line, $y = \alpha + \beta x$, of $y$ on $x$ based on the data, and then express $\alpha$ and $\beta$ as irreducible fractions.  
\newline
\textbf{Solution.}\newline
From the table above, $\bar{x} = 1, \;\bar{y} = 2, \; \sum_{i=1}^6(x_i-\bar{x})(y_i-\bar{y}) = 40,\; \sum_{i=1}^6(x_i-\bar{x})^2= 28$.  
Thus, 
$$\begin{aligned}
\beta &= \frac{40}{28} = \frac{10}{7} \\
\alpha &= 2 - \frac{10}{7} \times 1 = \frac{4}{7} \dots \Box
\end{aligned}$$
```{r, include=FALSE, echo=FALSE}
x <- c(-2, -1, 0, 2, 3, 4)
y <- c(-3, 0, 1, 3, 4, 7)
model <- lm(y ~ x)
summary(model)
10 / 7
4 / 7
```

\item[(1-3)] Find the coefficient of determination $R^2$ and then express it as an irreducible fraction. \newline
\textbf{Solution.} \newline

$$R^2 = r_{xy}^2 = \left(\frac{2\sqrt{105}}{21}\right)^2 = \frac{20}{21}\dots\Box$$
\item[(1-4)] Find the explained variation $\sum_{i=1}^6(y_{est,i} - \bar{y})^2$ and then express it as an irreducible fraction. \newline
\textbf{Solution.} \newline
Since $r_{xy}^2 = \frac{\sum_{i=1}^6 (y_{est,i} - \bar{y})^2}{\sum_{i=1}^6(y_i - \bar{y})^2}$, we have 
$$\sum_{i=1}^6(y_{est,i} - \bar{y})^2 = \frac{20}{21} \times 60 = \frac{400}{7}\dots \Box$$

\item[(1-5)] Find the unexplained variation $\sum_{i=1}^6(y_i - y_{est,i})^2$ and then express it as an irreducible fraction.\newline
\textbf{Solution.} \newline
Since $\sum_{i=1}^{6}\left(y_{i}-\bar{y}\right)^{2}=\sum_{i=1}^{6}\left(y_{e s t, i}-\bar{y}\right)^{2}+\sum_{i=1}^{6}\left(y_{i}-y_{e s t, i}\right)^{2}$, we have 
$$\begin{aligned}
\sum_{i=1}^{6}\left(y_{i}-y_{e s t, i}\right)^{2}&=\sum_{i=1}^{6}\left(y_{i}-\bar{y}\right)^{2}-\sum_{i=1}^{6}\left(y_{e s t, i}-\bar{y}\right)^{2} \\
&= 60 - \frac{400}{7} = \frac{20}{7} \dots \Box
\end{aligned}$$
\end{enumerate}



